D3064R0: Bringing the Laws of Physics, Computer-System Constraints, and Compilers to Bear on the OOTA Problem

### 2024-02-01 ootavacuous.tex
Add cbmc example for C++ non-determinism
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

@@

Listing~\ref{lst:Example Code for Evaluation of sdep}
shows a \co{herd7} thread \co{P0()}.
Is there a semantic dependency between the load from \co{x} on
line~3 to the store to \co{y} on line~9?

@@

@@

% @@@ TODO:
% Create nice bell graph for coe, or at least try!
% Construct interleaved OOTA examples (see sheets of paper).
% Check cmbc on nondeterministic i++.
% Use LKMM as check for dependencies?

>>>>

\subsection{Complex Semantic Dependencies}
\label{app:Complex Semantic Dependencies}

Listing~\ref{lst:Example Code for Evaluation of sdep}
shows a \co{herd7} thread \co{P0()}.
Is there a semantic dependency between the load from \co{x} on
line~3 to the store to \co{y} on line~9?
Answering this question requires solving a mathematical equation,
not all of which currently have known solutions.
However, this section will use a relatively simple equation combined
with restrictions on domain and range that permit \co{cbmc} to do
the job.

@@

@@

\subsection{C++ Non-Determinism}
\label{app:C++ Non-Determinism}

The C++ standard allows non-determinism, for example, the order of
invocation of side-effects in some circumstances.
Listing~\ref{lst:Code for cbmc-Based Evaluation of Non-Deterministic sdep}
shows an example leveraging side-effects in the parameter list shown on
line~37.

\begin{listing}[tbp]
@@ DisplayLitmus cbmc/sdep-nondet.c @@
\caption{Code for cbmc-Based Evaluation of Non-Deterministic sdep}
\label{lst:Code for cbmc-Based Evaluation of Non-Deterministic sdep}
\end{listing}

Running \co{cbmc} on this as follows:

\begin{quote}
\scriptsize
\begin{verbatim}
cbmc -DCBMC cbmc/sdep-nondet.c
\end{verbatim}
\end{quote}

Gives the result \co{VERIFICATION SUCCESSFUL}, showing that \co{cbmc}
does not model this non-determinism.
Which is not surprising, given that many of the safety-critical uses
to which \co{cbmc} is put would prohibit such non-determinism in their
code bases.

@@

% @@@ TODO:
% Construct interleaved OOTA examples (see sheets of paper).
% Use LKMM as check for dependencies?
